---
title: "lab 6 code"
author: "Sam Csik"
date: "2/14/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goals: 

- Read in spatial data
- Simplify polygons
- Add and transform projections  (st_transform, st_cars)
- Create a bunch of maps
- Join spatial data
- Find intersections of spatial data
- Interactive plots
- Create sf from lat/lon coordinates

```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(ggrepel)
library(ggspatial)
library(RColorBrewer)
library(raster)

```

###Example 1. Dams in California
```{r}
ca_eco <- read_sf(".", layer = "ca_eco") %>% 
  dplyr::select(US_L3NAME) %>% 
  rename(Region = US_L3NAME) %>% 
  st_simplify(dTolerance = 100) %>%  # if it's within 100 m of a line, it'll collapse it to simplify
  st_transform(crs = 4326)
```

```{r}
ca_counties <- read_sf(".", layer = "california_county_shape_file")

st_crs(ca_counties) = 4326  # assign a coordinate reference system to this
```

```{r}
ca_dams <- read_sf(".", layer = "California_Jurisdictional_Dams") %>% 
  rename(Condition = Condition_)

ca_dams$Condition <- fct_relevel(ca_dams$Condition, "Fair", "Satisfactory", "Unsatisfactory", "Poor")
```

MAPS!!
```{r}
plot(ca_eco)
plot(ca_counties)
```

Make a map with ggplot!
```{r}
color_count <- 13 # we need this many different colors for all our regions!

my_colors <- colorRampPalette(brewer.pal(10, "Set2"))(color_count) # make own color palette using RColorBrewer and specify that you want to split those colors into a gradient of 13

ggplot(ca_eco) +
  geom_sf(aes(fill = Region), # layer of ecoregions
          color = "NA", # gets rid of lines around each region
          show.legend = FALSE) +
  scale_fill_manual(values = my_colors) +
  geom_sf(data = ca_counties, # add another geom_sf polygon component with county lines
          fill = "NA", 
          color = "gray30", 
          size = 0.1) +
  geom_point(data = ca_dams, # add dams as points on map
             aes(x = Longitude, y = Latitude),
             size = 1,
             color = "gray10", 
             alpha = 0.5) +
  theme_minimal() +
  coord_sf(datum = NA) + # gets rid of lat and long coordinates on y and x axes
  labs(x = "", y = "") 

```

###Example 2. Dams in the Sierra Nevada eco-region
```{r}
sn <- ca_eco %>% 
  filter(Region == "Sierra Nevada") %>% 
  st_join(ca_dams)

ggplot(sn) +
  geom_sf(data = ca_counties, fill = "wheat3", color = "NA") +
  geom_sf(fill = "lemonchiffon4", color = "NA") +
  geom_point(aes(x = Longitude, y = Latitude),
             size = 0.5, 
             color = "red4")
```

###Example 3. Eco-regions for Santa Barbara County
```{r}
sb <- ca_counties %>% 
  filter(NAME == "Santa Barbara")

eco_clip <- st_intersection(ca_eco, sb)

ggplot(eco_clip) + 
  geom_sf(data = ca_counties, 
          fill = "gray90", color = "gray80",
          size = 0.2) +
  geom_sf(aes(fill = Region), color = "NA") +
  scale_fill_manual(values = c("darkolivegreen2", "darkolivegreen", "gold2")) +
  coord_sf(xlim = c(-121, -119), ylim = c(33.5, 35.5)) +
  geom_point(aes(x = -119.6982, y = 34.4208), size = 2) +
  geom_text(x = -119.6982, y = 34.35, label = "Santa Barbara") +
  theme_minimal() +
  theme(legend.position = c(0.5, 0.15))
```

###Example 4. Intro to interactive plots with tmap
```{r}
map_sb_eco <- tm_shape(eco_clip) + # make info into tm object and tell me what to do with it...
  tm_fill("Region", palette = "RdPu", alpha = 0.5) +
  tm_shape(ca_counties) + tm_borders()

tmap_mode("view") # sets tmap mode to interactive viewing

map_sb_eco

# leaflet::providers to find basemaps
# Example with a different basemap
tm_basemap("CartoDB.DarkMatter") +
  tm_shape(eco_clip) +
  tm_borders(col = "White")
```


###Example 5. Fault lines
```{r}
fault_lines <- read_sf(".", layer = "GMC_str_arc") %>% 
  st_transform(crs = 4326) %>%  # use if there is an exiting projection file
  separate(LTYPE, into = c("syn_ant", "certainty", "direction"), sep = ",")

ggplot() +
  geom_sf(data = ca_counties, fill = "black", color = "NA") +
  geom_sf(data = fault_lines, aes(color = syn_ant)) +
  theme_void()

# fault lines in SB county
sb_faults <- fault_lines %>% 
  st_intersection(sb)

ggplot() +
  geom_sf(data = sb) +
  geom_sf(data = sb_faults, aes(color = syn_ant))

# interactive
tm_basemap("CartoDB.DarkMatter") +
  tm_shape(sb) +
  tm_borders(col = "gray50", lwd = 2) +
  tm_shape(sb_faults) +
  tm_lines(col = "syn_ant", palette = c("orange", "purple"), lwd = 2)
```

###Example 6. Faceted Maps
```{r}
ggplot() +
  geom_sf(data = ca_counties, fill = "black", color = "NA") +
  geom_sf(data = fault_lines, aes(color = syn_ant)) +
  facet_wrap(~syn_ant)
```

###Example 7. Making spatial points
```{r}
ca_sites <- read_csv("cadfw_sensitive_sites.csv")

sites_sf <- st_as_sf(ca_sites, coords = c("LONDD", "LATDD"), crs = 4326)

ggplot() + 
  geom_sf(data = ca_counties, fill = "gray40") +
  geom_sf(data = sites_sf, aes(color = PRI_CODE), size = 0.3)
```

###Example 8. Chloropleth of CA countie by NUMBER of dams in each county
```{r}
intersection <- st_intersection(ca_dams, ca_counties) # check that space is lining up since different data sources may have slightly different zones

dams_per_county <- intersection %>% # make sure that county names match across data sets
  group_by(NAME) %>% 
  tally() 

ca_tot <- ca_counties %>% 
  st_join(dams_per_county) %>% 
  dplyr::select(NAME.x, n) %>% 
  rename(name = Name.x)

ca_tot$n[is.na(ca_tot$n)] <- 0
```

